Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection

### 2019-05-25 reports/paper1/paper.tex
Revise paper

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage{soul}%highlight changes

@@

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. \hl{Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.} A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved.
\end{abstract}

@@

Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves the \hl{acquisition and reconstruction of thousands} of projections of the sample. Speeding up the quality control process on the production line could be done by doing an inspection on a \hl{fewer number of projections by sacrificing accuracy} \citep{warnett2016towards, brierley2018optimized}.

A method was proposed to compare a \hl{single projection with a simulation of that projection and treating it as the ground truth.} This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not match up perfectly, producing incorrect inference.

An x-ray \hl{projection} of a 3D printed sample was obtained and compared with the simulation in an experiment. The procedure is shown in the methods section along with the description of the empirical null filter. In addition, the software development and simulation studies of the filter was discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $2000\times2000$ pixel \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. This object was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{young2000shading, munzenmayer2003enhancing} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

The 3D printed sample was scanned 20 times at a fixed angle. The 20 x-ray projections were spilt into 2. 19 random projections were held out. The remaining projection was used to compare with the simulation using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. In the \emph{aRTist} simulation, the software did a simulation as if the voids were not there. Numerical methods were used to align the simulated x-ray image to the obtained x-ray projection.

@@

Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the scan and \emph{aRTist}. A disagreement too big will classify that pixel as a positive result. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{scan}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan.

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated x-ray images of the 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable when working out the test statistics.

@@

The empirical null filter was tested to see if it can detect simulated defects from a $256\times 256$ contaminated image. A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$. A $30\times 30$ square defect was simulated. A kernel can capture the entire defect if its radius is large enough.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
  \caption{A $256\times 256$ contaminated Gaussian image with a $30 \times 30$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null. In this simulated example, it is about $r>54$. A kernel too small would treat the defects as null, making them difficult to detect.

@@

\begin{figure*}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $256 \times 256$ filtered contaminated Gaussian image with a $30\times 30$ square defect. Various kernel radiuses were investigated. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure*}

@@

In the experiment with the 3D printed sample, the x-ray image was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed object. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{../figures/inference/segment.JPG}
  \caption{The x-ray image was segmented further into 7 segments or ROI.}
  \label{fig:inference_segmentFurther}
\end{figure}

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{X-ray image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$. a) X-ray image with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure*}

@@

The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference. In the experiments, it was found that the FDR level is preserved after filtering.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $256\times 256$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plot summarise 100 repeated measurements of the timings.}
  \label{fig:inference_timing}
\end{figure*}

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements

@@

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection. A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.
\end{abstract}

@@

Quality control in additive manufacturing can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared with the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample. Speeding up the quality control process on the production line could be done by doing an inspection using a fewer number of projections by sacrificing accuracy \citep{warnett2016towards, brierley2018optimized}.

A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

An x-ray projection of a 3D printed sample was obtained and compared with the simulation in an experiment. The procedure is shown in the methods section along with the description of the empirical null filter. In addition, the software development and simulation studies of the filter was discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $2000\times2000$ pixel \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{young2000shading, munzenmayer2003enhancing} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

The projection of the 3D printed sample was obtained and repeated 20 times at a fixed angle. The 20 projections were spilt into 2. 19 random projections were held out. The remaining projection was used to compare with the simulation using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. In the \emph{aRTist} simulation, the software did a simulation as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection.

@@

Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the projection and the \emph{aRTist} projection. A disagreement too big will classify that pixel as a positive result. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.

The variance model, $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated projections of the sample. These replicated projections were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the \emph{aRTist} projection as the predictor variable when working out the test statistics.

@@

The empirical null filter was tested to see if it can detect simulated defects from a $\SI{256}{px}\times \SI{256}{px}$ contaminated image. A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$. A $\SI{30}{px}\times \SI{30}{px}$ square defect was simulated. A kernel can capture the entire defect if its radius is large enough.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
  \caption{A $\SI{256}{px}\times \SI{256}{px}$ contaminated Gaussian image with a $\SI{30}{px} \times \SI{30}{px}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null. In this simulated example, it is about $r>\SI{54}{px}$. A kernel too small would treat the defects as null, making them difficult to detect.

@@

\begin{figure*}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{px} \times \SI{256}{px}$ filtered contaminated Gaussian image with a $\SI{30}{px}\times \SI{30}{px}$ square defect. Various kernel radiuses were investigated. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was done at the 5\% FDR level. The box plot summarise the 100 repeated measurements of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure*}

@@

In the experiment with the 3D printed sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed sample. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{../figures/inference/segment.JPG}
  \caption{The x-ray projection was segmented further into 7 segments or ROI.}
  \label{fig:inference_segmentFurther}
\end{figure}

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{px}$. a) X-ray projection with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure*}

@@

The empirical null filter caters for inaccuracies made by \emph{aRTist} and voids in the order of millimetres were detectable. This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference. In the experiments, it was found that the FDR level is preserved after filtering.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $\SI{256}{px}\times \SI{256}{px}$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plot summarise 100 repeated measurements of the timings.}
  \label{fig:inference_timing}
\end{figure*}
